### 2014-03-09 src/results.Rnw
update

>>>>

\subsection{SDL vs Random selection}
\begin{figure*}[t]
<<sdl.x,fig.width=10, fig.height=10, out.width='.95\\linewidth', out.heigth='4in', echo=F, message=F, warn=F,fig.lp="fig:">>=
par(mfrow=c(2,2))
with(o.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Original SDL'))
with(o.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Original 1 per line'))
with(r.pit.all, plot(all.cov~TSDL.cov, pch='+', main='Randoop SDl'))
with(r.pit.all, plot(all.cov~l.1x1_per_line.cov, pch='+', main='Randoop 1 per line'))
@
\label{fig:sdl1}
\caption{Statement Deletion vs One per line.}
\end{figure*}
<<results='asis'>>=
oprand <- subset(stats.df,!grepl('^..op', rownames(stats.df)))

oprand.x <- subset(oprand,grepl('^.1x[0-9]+_per_', operator))
oprand.l <- subset(oprand,!grepl('^.1x[0-9]+_per_', operator))
@
